---
title: "LogisticReg"
output:
  pdf_document: default
  html_document: default
date: '2022-04-23'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rpart)
library(randomForest)
library(tree)
library(rpart.plot)
library(rattle)
set.seed(1)

```

# 1. Data Processing for model
Loading in data and splitting 

```{r}
processed_data <- read.csv("processed_new.csv")
tree_data <- processed_data[,c(28,65,86,88,180:191,196,197,199:203)]
col_names <- names(tree_data)
tree_data[,col_names] <- lapply(tree_data[,col_names] , factor)
str(tree_data)
```


## 1.1 Data Exploration

### ORIGIN_PLACE_TYPE and DESTIN_PLACE_TYPE 

```{r}
# plotting multiple bar plots
ggplot(tree_data, aes(fill=Label, x = ORIGIN_PLACE_TYPE)) +
  geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=0.5, size = rel(0.7)))
```


```{r}
# plotting multiple bar plots
ggplot(tree_data, aes(fill=Label, x = DESTIN_PLACE_TYPE)) +
  geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=0.5, size = rel(0.7)))
```

- We can see that ORIGIN_PLACE_TYPE and DESTIN_PLACE_TYPE can be remove since they did not help separating the target



```{r}
# plotting multiple bar plots
ggplot(tree_data, aes(fill=Label, x = Dest_Bus_Meter_Disc)) +
  geom_bar(position="dodge") + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=0.5, size = rel(0.7)))
```
- Season, trnsf
- Orig_Rail_Meter_Disc can be cont? Maybe coreleated with Dest_Rail_Meter_Disc

### Other

- Converting the label to 0 and 1
```{r}
tree_data$Label = as.numeric(as.character(factor(tree_data$Label,
                           levels = c('Bus', 'LRT'),
                           labels = c(0, 1))))
```

```{r}
library(InformationValue)
factor_vars <- col_names[col_names != "b"]  # get all categorical variables
all_iv <- data.frame(VARS=factor_vars, IV=numeric(length(factor_vars)), STRENGTH=character(length(factor_vars)), stringsAsFactors = F)  # init output dataframe
for (factor_var in factor_vars){
  all_iv[all_iv$VARS == factor_var, "IV"] <- InformationValue::IV(X=tree_data[, factor_var], Y=tree_data$Label)
  all_iv[all_iv$VARS == factor_var, "STRENGTH"] <- attr(InformationValue::IV(X=tree_data[, factor_var], Y=tree_data$Label), "howgood")
}
all_iv[(all_iv$STRENGTH == "Highly Predictive") | (all_iv$STRENGTH == "Somewhat Predictive"), ]
```


# 2. Implement Logistic Regression model


## Selecting those highly predictive column
```{r}
highpred <- all_iv[all_iv$STRENGTH == "Highly Predictive",]
highpred_col_name <- highpred$VARS
highpred_col_name <- c(highpred_col_name, "Label") #add abel
selected_tree_data <- tree_data[,highpred_col_name]

```

```{r}
train_ind <- sample(30491, 24393)
tree_train <- selected_tree_data[train_ind,]
tree_test <- selected_tree_data[-train_ind,]
predictor_name <- highpred_col_name[highpred_col_name != "Label"]

# tree_train <- tree_data[train_ind,]
# tree_test <- tree_data[-train_ind,]
# predictor_name <- col_names[col_names != "Label"]


X_train <- tree_train[,predictor_name]
X_test <- tree_test[,predictor_name]
y_train <- tree_train$Label
y_test <- tree_test$Label
```

```{r}
logregressor = glm(formula = Label ~ .,
                 family = binomial,
                 data = tree_train)
prob_pred_train = predict(logregressor, type = 'response', newdata = X_train)
```

```{r}
y_pred_train_logr = ifelse(prob_pred_train > 0.5, 1, 0)

prob_pred_test = predict(logregressor, type = 'response', newdata = tree_test)
y_pred_test_logr = ifelse(prob_pred_test > 0.5, 1, 0)
print(c(train_acc=mean(y_pred_train_logr==tree_train$Label), 
        test_acc=mean(y_pred_test_logr==tree_test$Label)))
```

```{r}
#Import required library
library(caret)
y_pred_test_logr <- factor(y_pred_test_logr)
y_true <- factor(tree_test$Label)
#Creating confusion matrix
example <- confusionMatrix(data=y_pred_test_logr, reference = y_true,positive = "1")
 
#Display results 
example
```

